The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2024-08-14 src/paper/theory.tex
Improve example application

In this specific case, there are two externalities to consider: (1) it costs the platform $F_i$ to serve an additional player on side $i$, and (2) the entry of a player on side $i$ increases the utility on side $j$ due to the presence of network effects.
Welfare is maximized when the price reflects the balance of these two factors.
\begin{proposition}
    \label{prop:welfare_max_entry_fees}
    The welfare-maximizing entry fees for side $i$ are characterized by
    \begin{align*}
        p_i^* = F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1}.
    \end{align*}
\end{proposition}

@@

Now let us examine what happens when the platform can set the entry fees unilaterally.
First, let us rewrite the platform's profit as a function of utilities, rather than the number of entrants:
\begin{align*}
    \pi_P(u_1, u_2) = \phi_1(u_1) [\alpha_1 \phi_2(u_2) ^ {\gamma_1} - u_1 - F_1] + \phi_2(u_2) [\alpha_2 \phi_1(u_1) ^ {\gamma_2} - u_2 - F_2].
\end{align*}
If the platform can set entry fees unilaterally, then it's problem can be viewed as choosing $u_1$ and $u_2$ to maximize this expression.
The next proposition characterizes the solution of this maximization problem.
\begin{proposition}
    \label{prop:unilateral_entry_fees}
    Assume that $\pi_P(u_1, u_2)$ is concave in $u_i$ and $u_2$.
    Then, the profit-maximizing entry fees for side $i$ are characterized by
    \begin{align*}
        p_i^u &= F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} + \frac{\phi_1(u_1)}{\phi'_1(u_1)} \\
              &= p_i^* + \frac{\phi_1(u_1)}{\phi'_1(u_1)}.
    \end{align*}
\end{proposition}

@@

Finally, let us consider the case when the platform and the entrants bargain over the value they generate.
Assume that $n_1$ and $n_2$ players have decided to enter on sides $1$ and $2$, respectively.
Furthermore, assume that players' bargaining weights are $\lambda_1, \lambda_2$ and $\lambda_P$.

The characteristic function of the game takes a similar form to that in \Cref{sec:many_sided}.
If the platform is not a member of a coalition, then the value that coalition can generate is zero.
Otherwise, it is simply the sum of the utilities of the two sides minus the cost of serving them.\footnote{
    Entry fees paid to the platform do not matter, as they are within-coalition transfers, and thus do not affect the total value.
}
This value, as a function of the number of entrants, is
\begin{align*}
    w(n_1, n_2) = n_1 \alpha_1 n_2^{\gamma_1} + n_2 \alpha_2 n_1^{\gamma_2} - F_1 n_1 - F_2 n_2.
\end{align*}

The share received by each type of player is then easily established using \Cref{prop:many_sided_weighted}.
\begin{proposition}
    \label{prop:bargaining_entry_fees}
    The weighted values of the various sides are
    \begin{alignat*}{4}
        \pi_P^b(n_1, n_2) &= \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_P^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_P^{b_2}} \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1}}_{\coloneqq S_P^{c_1}} n_1 F_1 &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2}}_{\coloneqq S_P^{c_2}} n_2 F_2 \\
        W_1^b(n_1, n_2) &= \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_1^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_1 \gamma_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_1^{b_2}}  \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1}}_{\coloneqq S_1^{c_1}} n_1 F_1 && \\
        W_2^b(n_1, n_2) &= \underbracket{\frac{\lambda_2\gamma_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_2^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_2^{b_1}} \alpha_2 n_2 n_1^{\gamma_2} && &&- \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2}}_{\coloneqq S_2^{c_2}} n_2 F_2.
    \end{alignat*}
\end{proposition}

Total welfare $w(n_1, n_2)$ can be divided into four parts: utility generated by side $1$ and $2$, and the costs of serving side $1$ and $2$.
Each side's share of these parts is given by $S_i^{b_1}, S_i^{b_2}, S_i^{c_1}$ and $S_i^{c_2}$, respectively.
As it turns out, these shares only depend on the bargaining weights ($\lambda_P, \lambda_1, \lambda_2$) and the network effects ($\gamma_1, \gamma_2$), but not on the actual number of entrants.\footnote{
    This is due to the characteristic function being a polynomial of the number of entrants.
    Just like in \Cref{sec:power_function_example}, each constituent of the polynomial are divided in a constant proportion.
}
Furthermore, all of these shares are increasing in one's own bargaining weight, and decreasing in the others' weights.
Finally, and perhaps most interestingly, the share of side $i$ from the value generated on side $j$ is also increasing in $\gamma_j$.
This means that if players on side $i$ are less substitutable (or, equivalently, more complementary) in terms of contributing to the utility of the other side, then they will receive a larger share of the value generated there.

These utilities are remarkably similar in structure to those obtained in the welfare maximizing case.
The main difference is that each part (both costs and positive utilities) is reweighted, and side $i$ only receives a fraction of it.
It is also worth noting that $W_i^b(n_1, n_2) < W_i^*(n_1, n_2)$, and, as a consequence, entry is lower than what would be socially optimal.\footnote{
    The easiest way to see it is that in the welfare-maximizing case the platform's profit is negative, while in the bargaining case it is positive.
    Therefore, fringe utilities must be lower in the latter case.
}
These similarities and differences are examined in more detail in the next subsection.

For better comparison, let us also derive implied entry fees and utilities.\footnote{
    If one wished to close the model, the number of entrants in equilibrium could be obtained by solving the system of equations $n_i = \phi_i(u_i(n_1, n_2)), n \in \{1, 2\}$, just like in the other cases.
}
The latter is simply average welfare, i.e.:
\begin{align*}
    u_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} + \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} - \frac{\lambda_i}{\lambda_P + \lambda_i} F_i.
\end{align*}
Finally, the implied entry fees can be calculated from the equation $u_i = \alpha_i n_j^{\gamma_i} - p_i$, giving
\begin{align*}
    p_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i} F_i - \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} + \frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i}.
\end{align*}

@@

Let us now compare the outcomes of the three cases described in the previous subsections.
To highlight the similarity to \textcite{armstrong2006competition}, I will first consider the case of linear network effects.
Furthermore, for simplicity of exposition, I start by examining the non-weighted Shapley value before moving on to the weighted value.

Assume that network effects are linear, i.e. $\gamma_i = 1$ for $i \in \{1, 2\}$.
Also, focus on non-weighted Shapley values ($\lambda_P = \lambda_1 = \lambda_2 = 1$).
From the previous results, the entry fees for side $i$ are
\begin{align*}
    p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j n_j n_i}_{(2)}, \\
    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j n_j n_i}_{(2)} + \underbracket{n_i (\phi_i^{-1})'(n_i)}_{(3)} \\
    p_i^b &= \underbracket{\frac{1}{2} F_i}_{(1)} - \underbracket{\frac{1}{3} \alpha_j n_j n_i}_{(2)} + \underbracket{\frac{2}{3} \alpha_i n_j}_{(4)},
\end{align*}
for the welfare-maximizing, unilateral price setting and bargaining cases, respectively.

All of these expressions bear some similarities to each other in that the price is somehow related to the externalities that an entrant imposes on the other players.
In fact, the welfare-maximizing price is just that: the cost of serving one additional player (1) and the positive externality imposed on the other side (2).
The unilateral pricing case also includes these two factors in full, but also adds a third factor, related to the elasticity of entry (3).
Namely, the platform extracts some of the surplus generated by the entrants, and the surplus it wants to extract depends on the elasticity of entry, $\phi'_i(u_i)$.
It is the same mechanism that leads to markups in a simple monopolistic pricing model.

The bargaining case also includes the first two factors, albeit they are somewhat different.
As opposed to the first two cases, the price only contains some fraction of the externalities, while the rest is shared with the platform and the other side.\footnote{
    Due to the linearity of the model and the symmetry of the Shapley value, each part of the value is shared equally between players who participate in producing them.
    This is the reason why, for example, the platform and the firms share the cost of serving the entrants (1) equally, or why all three types of players share the value generated on a given side (2) equally.
}
Furthermore, some part of the welfare generated on side $i$ is also shared with the other players, and thus appears in the price (4).
This is in contrast to both the welfare-maximizing and unilateral pricing cases, where the entry fee did not depend on the actual utility that was materialized on the given side.
Therefore, bargaining introduces some interesting departures from both the welfare-maximizing and unilateral pricing cases.

Now let us consider non-linear network effects.
The welfare-maximizing, unilateral pricing and bargaining entry fees are as follows:
\begin{align*}
    p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)}, \\
    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
    p_i^b &= \underbracket{\frac{1}{2} F_i}_{(1)} - \underbracket{\frac{\gamma_j}{2 + \gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{\frac{1 + \gamma_i}{2 + \gamma_i} \alpha_i n_j^{\gamma_i}}_{(4)}.
\end{align*}
For the most part, the intuition is the same as in the linear case.
In fact, in the welfare-maximizing and unilateral pricing cases, nothing changes apart from the marginal externality imposed on the other side (2) being slightly different.
On the other hand, there is one important difference in the bargaining case.
In the linear case, the terms related to the value generated on each side were shared between the players in a constant proportion, independent of the model parameters.
In this non-linear case, however, these shares depend on the shape of the network effects.
In particular, when side $i$'s network externality on side $j$ is more convex (e.g. firms on side $i$ are less substitutable), then it receives a larger share of the value generated on the other side.
This is signified by the fact that the coefficient of side $i$'s network externality, $\frac{\gamma_j}{2 + \gamma_j}$, is increasing in $\gamma_j$.
This result demonstrates that bargaining outcomes are not just a split of the value, but also take into account the shape of the network effects.

@@

In the case of the cost of serving one additional player (1), the addition of bargaining weights simply leads to players sharing the cost in a constant proportion, according to their weights.\footnote{
    This is because this term is linear in the number of entrants.
}
The higher the weight, the larger the share for any given player.
While the latter observation is true for non-linear terms, as well, the influence of the weights is more complex for those.
Namely, it also depends on the shape of value function.
For example, in term (2), $\lambda_i$ interacts with the parameter determining the shape of the network effects, $\gamma_j$
Therefore, the weighted value is more than just a simple reweighting of the non-weighted value, and its effects can be quite complex depending on the assumptions on the value function.

Whether bargaining leads to a higher or lower total welfare depends on the parameters of the model.
For example, if $\lambda_P$ is very high, then $p_i^b > p_i^u > p_i^*$, leading to fewer firms entering and lower total surplus not only than the welfare-maximizing case, but also than the unilateral pricing case.
That is, it can happen that everybody looses from bargaining.\footnote{
    In such a case, the platform would like to set lower entry fees than what it can achieve via bargaining.
    While in some settings it makes sense to assume that it can do that, in others, commitment issues might prevent it from doing so.
}
On the other hand, if $\lambda_P$ is sufficiently low, then one can find weights $\lambda_1, \lambda_2$, such that $p_i^u > p_i^b > p_i^*$.
In such a case, the platform would like to set higher entry fees than what it can achieve via bargaining for both sides.
Furthermore, the total welfare under bargaining is between the welfare-maximizing and unilateral pricing cases.
Therefore, whether bargaining leads to higher or lower welfare than unilateral pricing depends on model parameters.
The platform, however, always achieves a (weakly) lower profit than if it could set the entry fees unilaterally.

Finally, it is always true that $p_1^b < p_1^*$ or $p_2^b < p_2^*$.
The reason is that the platform's profit is always non-negative in the bargaining case, while it is negative in the welfare-maximizing case.
This also implies that the total welfare is strictly lower under bargaining than in the welfare maximizing benchmark.
Therefore, while bargaining can be welfare-improving compared to unilateral price setting, it can not achieve the highest possible total utility.\footnote{
    One could argue that the welfare maximizing case is not a realistic benchmark anyway, as it assumes that the platform is making a loss.
}

@@

Finally, I demonstrate how the proposed framework can be applied in practice by
examining the two-sided platform model based on \textcite{armstrong2006competition}.
I show that the resulting entry fees have some similarities to the welfare-maximizing and unilateral price setting benchmarks, but also differ in some important ways.
In particular, the externalities that players entrants impose on the platform (cost of serving) and the other side (network externalities) are not fully incorporated into the entry fees, but shared across the affected players.
Similarly, the value generated on each side also factors into the entry fee, contrary to the benchmark cases where it does not directly matter.
This suggests, in situations where bargaining between players is plausible, certain effects might be overrepresented or missed if one assumes unilateral price-setting.

>>>>

In this specific case, there are two externalities to consider: (1) it costs the platform $F_i$ to serve an additional player on side $i$, and (2) the entry of a player on side $i$ increases the utility on side $j$ due to the presence of network effects.
Welfare is maximized when the price reflects the balance of these two factors.
\begin{proposition}
    \label{prop:welfare_max_entry_fees}
    The welfare-maximizing entry fees for side $i$ are characterized by
    \begin{align}
        p_i^* = F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1}.  \label{eq:welfare_max_entry_fees}
    \end{align}
\end{proposition}

@@

Now let us examine what happens when the platform can set the entry fees unilaterally.
First, let us rewrite the platform's profit as a function of utilities, rather than the number of entrants:
\begin{align*}
    \pi_P(u_1, u_2) = \phi_1(u_1) [\alpha_1 \phi_2(u_2) ^ {\gamma_1} - u_1 - F_1] + \phi_2(u_2) [\alpha_2 \phi_1(u_1) ^ {\gamma_2} - u_2 - F_2].
\end{align*}
If the platform can set entry fees unilaterally, then it's problem can be viewed as choosing $u_1$ and $u_2$ to maximize this expression.
The next proposition characterizes the solution of this maximization problem.
\begin{proposition}
    \label{prop:unilateral_entry_fees}
    Assume that $\pi_P(u_1, u_2)$ is concave in $u_i$ and $u_2$.
    Then, the profit-maximizing entry fees for side $i$ are characterized by
    \begin{align}
        p_i^u &= F_i - \alpha_j \gamma_j n_j n_i^{\gamma_j - 1} + \frac{\phi_1(u_1)}{\phi'_1(u_1)}  \label{eq:unilateral_entry_fees} \\
              &= p_i^* + \frac{\phi_1(u_1)}{\phi'_1(u_1)}.  \nonumber
    \end{align}
\end{proposition}

@@

Finally, let us consider the case when the platform and the entrants bargain over the value they generate.
Suppose that $n_1$ and $n_2$ players have decided to enter on sides $1$ and $2$, respectively.
Furthermore, assume that players' bargaining weights are $\lambda_1, \lambda_2$ and $\lambda_P$.

The characteristic function of the game takes a similar form to that in \Cref{sec:many_sided}.
If the platform is not a member of a coalition, then that coalition can generate no value.
Otherwise, the value of the coalition is the sum of the utilities of the two sides minus the cost of serving them:\footnote{
    Entry fees paid to the platform do not matter as they are within-coalition transfers, and thus do not affect the total value.
}
\begin{align*}
    w(n_1, n_2) = n_1 \alpha_1 n_2^{\gamma_1} + n_2 \alpha_2 n_1^{\gamma_2} - F_1 n_1 - F_2 n_2.
\end{align*}

The share received by each type of player can then be established using \Cref{prop:many_sided_weighted}.
\begin{proposition}
    \label{prop:bargaining_entry_fees}
    The weighted values of the various sides are
    \begin{alignat*}{4}
        \pi_P^b(n_1, n_2) &= \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_P^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_P^{b_2}} \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1}}_{\coloneqq S_P^{c_1}} n_1 F_1 &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2}}_{\coloneqq S_P^{c_2}} n_2 F_2 \\
        W_1^b(n_1, n_2) &= \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_1^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_1 \gamma_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_1^{b_2}}  \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1}}_{\coloneqq S_1^{c_1}} n_1 F_1 && \\
        W_2^b(n_1, n_2) &= \underbracket{\frac{\lambda_2\gamma_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_2^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_2^{b_1}} \alpha_2 n_2 n_1^{\gamma_2} && &&- \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2}}_{\coloneqq S_2^{c_2}} n_2 F_2.
    \end{alignat*}
\end{proposition}

Total welfare $w(n_1, n_2)$ can be divided into four parts: utility generated by sides $1$ and $2$, and the costs of serving sides $1$ and $2$.
Each side's share of these parts is given by $S_i^{b_1}, S_i^{b_2}, S_i^{c_1}$ and $S_i^{c_2}$, respectively.
As it turns out, these shares only depend on the bargaining weights ($\lambda_P, \lambda_1, \lambda_2$) and the network effects ($\gamma_1, \gamma_2$), but not on the actual number of entrants.\footnote{
    This is due to the characteristic function being a polynomial of the number of entrants.
    Just like in \Cref{sec:power_function_example}, each constituent of the polynomial is divided in a constant proportion.
}
Furthermore, all of these shares are increasing in one's own bargaining weight, and decreasing in the others' weights.
Finally, and perhaps most interestingly, the share of side $i$ from the value generated on side $j$ is also increasing in $\gamma_j$.
This means that if players on side $i$ are less substitutable (or, equivalently, more complementary) in terms of contributing to the utility of the other side, then they will receive a larger portion of the value generated there.

These expressions for welfare are remarkably similar in structure to those obtained in the welfare maximizing case.
The main difference is that each part (both costs and positive utilities) is reweighted, and either side only receives a fraction of it.
It is also worth noting that $W_i^b(n_1, n_2) < W_i^*(n_1, n_2)$, and, as a consequence, entry is lower than what would be socially optimal.\footnote{
    The easiest way to see it is this in the welfare-maximizing case the platform's profit is negative, while in the bargaining case it must be non-negative.
    Therefore, fringe utilities must be lower in the latter case.
}
These similarities and differences are examined in more detail in the next subsection.
%TODO: check if it is true for both sides

For making comparisons easier, let us also derive implied entry fees and utilities.\footnote{
    If one wished to close the model, the number of entrants in equilibrium could be obtained by solving the system of equations $n_i = \phi_i(u_i(n_1, n_2)), n \in \{1, 2\}$, just like in the other cases.
}
The latter is simply average welfare, i.e.
\begin{align*}
    u_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i} + \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} - \frac{\lambda_i}{\lambda_P + \lambda_i} F_i.
\end{align*}
Implied entry fees on the other hand can be calculated from the equation $u_i = \alpha_i n_j^{\gamma_i} - p_i$, giving
\begin{align}
    p_i^b(n_1, n_2) &= \frac{\lambda_i}{\lambda_P + \lambda_i} F_i - \frac{\lambda_i \gamma_j}{\lambda_P + \lambda_j + \lambda_i\gamma_j} \alpha_j n_j n_i^{\gamma_j - 1} + \frac{\lambda_P + \lambda_j\gamma_i}{\lambda_P + \lambda_i + \lambda_j\gamma_i} \alpha_i n_j^{\gamma_i}.  \label{eq:bargaining_entry_fees}
\end{align}

@@

Let us now compare the outcomes of the three cases described in the previous sections.
To highlight the similarity to \textcite{armstrong2006competition}, I first consider the case of linear network effects.
Furthermore, for simplicity of exposition, I start by examining the non-weighted Shapley value before moving on to the weighted value.

Therefore, first assume that network effects are linear, i.e. $\gamma_i = 1$ for $i \in \{1, 2\}$ and that all players have equal weights ($\lambda_P = \lambda_1 = \lambda_2 = 1$).
From \Cref{eq:welfare_max_entry_fees,eq:unilateral_entry_fees,eq:bargaining_entry_fees}, the entry fees for side $i$ are
\begin{align*}
    p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j n_j n_i}_{(2)}, \\
    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j n_j n_i}_{(2)} + \underbracket{n_i (\phi_i^{-1})'(n_i)}_{(3)} \\
    p_i^b &= \underbracket{\frac{1}{2} F_i}_{(1)} - \underbracket{\frac{1}{3} \alpha_j n_j n_i}_{(2)} + \underbracket{\frac{2}{3} \alpha_i n_j}_{(4)},
\end{align*}
for the welfare-maximizing, unilateral price setting and bargaining cases, respectively.

All of these expressions bear some similarities to each other in that the price is related to the externalities that an entrant imposes on the other players.
In fact, the welfare-maximizing price is just that: the cost of serving one additional player (1) and the positive externality imposed on the other side (2).
The unilateral pricing case also includes these two factors in, as well as a third factor, which related to the elasticity of entry (3).
Namely, the platform extracts some of the surplus generated by the entrants, and the surplus it wants to extract depends on the elasticity of entry, $\phi'_i(u_i)$.
It is the same mechanism that leads to markups in a simple monopolistic pricing model.

The bargaining case also includes factors (1) and (2), albeit they appear somewhat differently.
As opposed to the first two cases, the price only contains some fraction of these externalities, with the rest being shared with the platform and the other side.\footnote{
    Due to the linearity of the model and the symmetry of the Shapley value, each part of the value is shared equally between players who participate in producing them.
    This is the reason why, for example, the platform and the firms share the cost of serving the entrants (1) equally, and why all three types of players share the value generated on a given side (2) equally.
}
Furthermore, a part of the welfare generated on side $i$ (4) is also shared with the other players, and thus appears in the price.
This is in contrast to both the welfare-maximizing and unilateral pricing cases, where the entry fee for a given side does not depend on the actual utility that was materialized on that side.
Therefore, bargaining introduces some interesting departures from both the welfare-maximizing and unilateral pricing cases.

Now let us consider more general, non-linear network effects.
The welfare-maximizing, unilateral pricing and bargaining entry fees are as follows:
\begin{align*}
    p_i^* &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)}, \\
    p_i^u &= \underbracket{F_i}_{(1)} - \underbracket{\alpha_j \gamma_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{n_i \kappa'_i(n_i)}_{(3)} \\
    p_i^b &= \underbracket{\frac{1}{2} F_i}_{(1)} - \underbracket{\frac{\gamma_j}{2 + \gamma_j} \alpha_j n_j n_i^{\gamma_j - 1}}_{(2)} + \underbracket{\frac{1 + \gamma_i}{2 + \gamma_i} \alpha_i n_j^{\gamma_i}}_{(4)}.
\end{align*}
For the most part, the intuition is the same as in the linear case.
In fact, in the welfare-maximizing and unilateral pricing cases, nothing changes apart from the marginal externality imposed on the other side (2) being slightly different.
On the contrary, there is an important difference in the bargaining case.
Under linear network effects, the terms related to the value generated on each side were shared between the players in a constant proportion, independent of the model parameters.
In this non-linear case, however, these shares do depend on the shape of the network effects.
In particular, when side $i$'s network externality on side $j$ is more convex, the former receives a larger share of the value generated on the other side.\footnote{
    The corresponding coefficient, $\frac{\gamma_j}{2 + \gamma_j}$, is increasing in $\gamma_j$.
}
This demonstrates that bargaining outcomes are not just a fixed split of the value, but also take into account the shape of the network effects.

@@

For the cost of serving the players (1), the addition of bargaining weights simply leads to players sharing that cost in a constant proportion, according to their weights.\footnote{
    This is because this term is linear in the number of entrants.
}
The higher the weight, the larger the share for any given player.
While the latter observation is true for non-linear terms, as well, the influence of the weights is more complex in their case.
Namely, it also depends on the shape of value function.
For example, in term (2), $\lambda_i$ interacts with the parameter determining the shape of the network effects, $\gamma_j$
Therefore, the weighted value is more than just a simple reweighting of the non-weighted value, and its effects can be quite complex depending on the shape of the value function.

Whether bargaining leads to a higher or lower total welfare in comparison to unilateral price setting depends on the parameters of the model.
For example, if $\lambda_P$ is high enough, then $p_i^b > p_i^u > p_i^*$, leading to fewer firms entering and lower total surplus not only than the welfare-maximizing case, but also than the unilateral pricing case.
In other words, it can happen that everybody looses from bargaining.\footnote{
    In such a case, the platform would like to set lower entry fees than what it can achieve via bargaining.
    This might be a realistic constraint in settings with commitment issues.
}
On the other hand, if $\lambda_P$ is sufficiently low, then one can always find weights $\lambda_1, \lambda_2$, such that $p_i^u > p_i^b > p_i^*$.
In such a case, the platform would like to set higher entry fees than what it can achieve via bargaining for both sides of the market.
As a consequence, the total welfare under bargaining is between the welfare-maximizing and unilateral pricing cases.
Therefore, whether bargaining leads to higher or lower welfare than unilateral pricing depends on model parameters.
The platform, however, always achieves a (weakly) lower profit than if it could chose the entry fees itself.

Finally, it is always true that $p_1^b < p_1^*$ or $p_2^b < p_2^*$.
The reason is that the platform's profit is always non-negative in the bargaining case, while it is negative in the welfare-maximizing case.
This also implies that the total welfare is strictly lower under bargaining than in the welfare maximizing benchmark.
Therefore, while bargaining can be welfare-improving compared to unilateral price setting, it can not achieve the highest possible total utility.\footnote{
    One could argue that the welfare maximizing case is not a realistic benchmark anyway, as the platform is operating at a loss.
}

@@

Finally, I demonstrate how the proposed framework can be applied in practice by
examining the two-sided platform model based on \textcite{armstrong2006competition}.
I show that the resulting entry fees have some similarities to the welfare-maximizing and unilateral price setting benchmarks, but also differ in some important ways.
In particular, the externalities that players entrants impose on the platform (cost of serving) and the other side (network externalities) are not fully incorporated into the entry fees, but shared across the affected players.
Similarly, the value generated on each side also factors into the entry fee, contrary to the benchmark cases where it does not directly matter.
This suggests, in situations where bargaining between players is plausible, certain effects might be overrepresented or missed if one assumes unilateral price setting.
